Caribou Demographic Projection - interesting & informative title TBD

### 2023-01-20 analysis/paper/paper.Rmd
work on initial sensitivity analysis in progress.

* ensure that INF_saf_INF_r_JAGS_extentTime.txt and INF_saf_INF_r_JAGS_expSurvival2.txt are identical except for the survival observation model. Or better yet, write code to sub in correct survival model more elegantly.
* note various bits of truncation in the JAGS code to ensure R and S remain between 0 and 1 (not guaranteed given log link). Not all documented in this explanation. Bayesian wizard might know a better way. Or at least know how to explain.
* note Eacker survival method gives biased results in years when <12 months of survival data is available.
* Note I am dropping survival information for animals that are not alive at the beginning of a year to deal with censoring issues. There is probably some more elegant way to deal with this, but it won't make any difference as long as the collar deployment month is set to 1.
* add references to documentation of popGrowthJohnson and other caribouMetrics functions.

@@

Table 1. Example ranges. Ontario demographic information from [@mnrf_state_2014]. If two numbers given for Anthropogenic disturbance they are BEAD 2010 and 2015.
*note that we've had some input on monitoring numbers from NL, BC, ON (and MB pending), so some of them may also be willing to give us case study examples to use here?

@@

Table 2. Monitoring scenarios adapted from [@rettie_summary_2017]. *removed the second collar column (assuming minimum=initial) and removed collaring month and duration, but added renewal interval, and hoping to also be able to provide some sort of example of real ranges that are similar to the scenario. 
*Monitoring WG input from BC, ON, NL, (MB pending): lots of detail provided but generally those numbers suggest we could try values of ~3-10 [e.g. 3,6,9?] for the cow multiplier, 5-50 for collars [e.g. 5,10,20,40,60?], [not sure about renewal interval, but see SaraM email for some insights]. We know (e.g. from the MonitoringWG perspectives report/update to Rettie summary) that number of years of monitoring can be as low as 2 or as many as 20+
```{r}
tbl <- "Years|Collars|cow multiplier|collar renewal interval|example
3|30|3|1|ex range?
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```

@@

TO DO: Fire scenarios?

@@

## Example figure

@@

```{r fig1, fig.cap="Example figure.", cache=TRUE}
#knitr::include_graphics(here::here("figs/Figure1_Example.png"))

>>>>

* ensure that INF_saf_INF_r_JAGS_extentTime.txt and INF_saf_INF_r_JAGS_expSurvival2.txt are identical except for the survival observation model. Or better yet, write code to sub in correct survival model more elegantly.
* note various bits of truncation in the JAGS code to ensure R and S remain between 0 and 1 (not guaranteed given log link). Not all documented in this explanation. Bayesian wizard might know a better way. Or at least know how to explain.
* note Eacker survival method gives biased results in years when <12 months of survival data is available.
* Note I am dropping survival information for animals that are not alive at the beginning of a year to deal with censoring issues. There is probably some more elegant way to deal with this, but it won't make any difference as long as the collar deployment month is set to 1.
* add references to documentation of popGrowthJohnson and other caribouMetrics functions.
* consider & comment on alternative choices made in this example https://poissonconsulting.shinyapps.io/bboushiny/. Follow Eacker example in all particulars, change some aspects, or do comparisons?

@@

Table 1. Example ranges. Ontario demographic information from [@mnrf_state_2014]. If two numbers given for Anthropogenic disturbance they are BEAD 2010 and 2015.
*note that we've had some input on monitoring numbers from NL, BC, ON (and MB pending), so some of them may also be willing to give us case study examples to use here? Note can get details about SK1 from Phil's report.

@@

relevant refs: [@rettie_summary_2017];?

```{r monitoringScenarios, echo=FALSE,message=FALSE}

source(here::here("analysis/scripts/formatScenarios.R"))

knitr::kable(tbl,caption="Monitoring scenarios parameters and values (example values to stimulate discussion - what should these numbers be and why?)")
```

*Monitoring WG input from BC, ON, NL, (MB pending): lots of detail provided but generally those numbers suggest we could try values of ~3-10 [e.g. 3,6,9?] for the cow multiplier, 5-50 for collars [e.g. 5,10,20,40,60?], [not sure about renewal interval, but see SaraM email for some insights]. We know (e.g. from the MonitoringWG perspectives report/update to Rettie summary) that number of years of monitoring can be as low as 2 or as many as 20+

@@

TO DO: Fire scenarios? Add high fire scenario in appendix of one by one sensitivity checks.

TO DO: run low initial population size scenario, put in appendix of one by one sensitivity checks.

TO DO: calculate change in anthro disturbance over 5 yrs across ranges to get realistic distribution of numbers of this & justify choice of parameters. run alternative scenario to put in one by one sensitivity appendix.

```{r fig1, fig.cap="Anthropogenic disturbance and monitoring scenarios (examples to stimulate discussion).", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/distScnscmult3ay1aSf1.png"))

@@

TO DO: consider showing results in terms of average number of collars deployed per year rather than target # and renewal interval.

@@
